---
title: "lab1"
author: "Nakyung, Songyi, Will"
date: "2025-01-08"
output: html_document
---

```{r}
library(here)
library(rio)
d <- rio::import(here::here("data", "rstats_tweets.rds"), setclass = "tbl_df")
```

# Initial Exploration

```{r}
library(tidyverse)
ggplot(data = d, aes(x = display_text_width)) +
  geom_histogram(aes(y = ..density..), binwidth = 5, color = "black", fill = "skyblue", alpha = 0.5) +
  theme_minimal()
```

Small binwidth: Useful for emphasizing detailed distributions and identifying outliers.

```{r}
ggplot(data = d, aes(x = display_text_width)) +
  geom_histogram(aes(y = ..density..), binwidth = 20, color = "black", fill = "skyblue", alpha = 0.5) +
  theme_minimal()
```

Medium binwidth: Provides a balanced visualization that highlights major patterns.

```{r}
ggplot(data = d, aes(x = display_text_width)) +
  geom_histogram(aes(y = ..density..), binwidth = 100, color = "black", fill = "skyblue", alpha = 0.5) +
  theme_minimal()
```

Large binwidth: Suitable for capturing the overall structure of the data.

```{r}
ggplot(d, aes(display_text_width)) +
  geom_density(fill = "gray20")
```

Default bandwidth for density plots: Naturally represents the distribution, making it easier to understand broader trends.

```{r}
ggplot(d, aes(display_text_width)) +
  geom_density(bw = 0.2, fill = "gray20")
```

Small bandwidth for density: Emphasizes fine-grained patterns


# Plot 
```{r}
library(tidytext)
plot <- d %>% 
  unnest_tokens(word, text)
plot
```

```{r}
plot %>% 
  anti_join(stop_words) %>% 
  count(word, sort = TRUE) %>% 
  mutate(word = reorder(word, n)) %>%
  slice(1:15) %>% 
  ggplot(aes(n, word)) +
    geom_col(fill = "cornflowerblue")
```





